Epistemic Semantics in Guarded String Models\thanks{Thanks guys.}

### 2021-01-15 tex/pdraft.tex
49 states and 110 edges

Sentences are parsed with a chart parser for categorial grammar.  The semantics for
complex phrases are obtained by application of semantic translations, accompanied by
beta reductions that eliminate all lambdas in logical forms for clauses.  In
consequence, the semantic term translating a sentence is an Epi\textsc{Kat} logical term.  Such
a term designates a set of possible words (guarded strings).  By way of example,
\exi{three}{a} is an English sentence with conjunction and several levels of clausal
embedding.  Using the grammar and parser, the sentence is mapped to the term in
\exi{three}{b}. \exi{three}{c} shows a simplified logical from constructed form
\exi{three}{b} using logical equivalences. Either term is compiled in an
implementation of the finite state calculus to a finite state machine with 10 states
and 23 edges, which accepts a countably infinite set of worlds.\footnote{ Machine
  sizes need not be small, especially as the cardinality of $\sf{B}$ increases.  A
  certain Epi\textsc{Kat} model with fourteen primitive Booleans has the set of worlds
  representented by a finite state machine with 184,794 states and 257,881 edges.}  In
this way the methodology ``directly'' represents the set of worlds denoted by
\exi{three}{a}.

>>>>

Sentences are parsed with a chart parser for categorial grammar.  The semantics for
complex phrases are obtained by application of semantic translations, accompanied by
beta reductions that eliminate all lambdas in logical forms for clauses.  In
consequence, the semantic term translating a sentence is an Epi\textsc{Kat} logical term.  Such
a term designates a set of possible words (guarded strings).  By way of example,
\exi{three}{a} is an English sentence with conjunction and several levels of clausal
embedding.  Using the grammar and parser, the sentence is mapped to the term in
\exi{three}{b}. \exi{three}{c} shows a simplified logical from constructed form
\exi{three}{b} using logical equivalences. Either term is compiled in an
implementation of the finite state calculus to a finite state machine with 49 states
and 110 edges, which accepts a countably infinite set of worlds.\footnote{ Machine
  sizes need not be small, especially as the cardinality of $\sf{B}$ increases.  A
  certain Epi\textsc{Kat} model with fourteen primitive Booleans has the set of worlds
  representented by a finite state machine with 184,794 states and 257,881 edges.}  In
this way the methodology ``directly'' represents the set of worlds denoted by
\exi{three}{a}.
